\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex

The impact of the version on success rate is (significant,not significant). 
The impact of the environment on success rate is (significant,not significant). 
% SUCCESS
% TODO: impact of version on success (chi squared?.. Serge might be wrong on this) 
% TODO: impact of env on success (chi squared?.. Serge might be wrong on this)

Talk about why we chose to assign the max time of 40 minutes to did not finish. 
The impact of the version on time to completion is (significant,not significant). 
The impact of the environment on time to completion is (significant,not significant).
Figure~\ref{fig:time_to_success_clamped}
%%% RIGHT CLAMP TIME 
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:01 \\
	E2-NEW & 18/19 & 95\% & 3:32 \\
	E2-OLD & 16/19 & 84\% & 5:00 \\
	E3-NEW & 13/20 & 65\% & 20:56 \\
	E3-OLD & 10/20 & 50\% & 40:08 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
The impact of the version on active time is (significant,not significant). 
The impact of the environment on active time is (significant,not significant).
%%% RIGHT CLAMP ACTIVE TIME 
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
{\color{red} MAKE THIS FOR ACTIVE TIME}
}
\label{fig:active_time_clamped}
\end{figure}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
	\end{tabular}
\caption{overall time} 
\label{table:overall_time}
\end{table}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 23\% & 52\% & 23\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 17\% & 58\% & 25\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 27\% & 40\% & 29\% & 3\% \\
	E3 & 20\% & 57\% & 21\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

@@

% impacts of making bridge page collapsed 
This is unclear. And people didn't really see our advice that we put on the page.

>>>>

Talk about why we chose to assign the max time of 40 minutes to did not finish. 
The impact of the version on time to completion is (significant,not significant). 
The impact of the environment on time to completion is (significant,not significant).
Figure~\ref{fig:time_to_success_clamped}

%stats
impact of version on success: not significant (W = 5.5, p-value = 0.8248)
impact of version on time to success: not significant (W = 1399, p-value = 0.1175)

impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
	E1-OLD & 19/19 & 100\% & 1:01 \\ %medians of only finished: 1:01
	E2-NEW & 18/19 & 95\% & 3:32 \\ %medians of only finished: 3:22
	E2-OLD & 16/19 & 84\% & 5:00 \\ %medians of only finished: 3:13
	E3-NEW & 13/20 & 65\% & 20:56 \\ %medians of only finished: 12:38
	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

@@

Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
	\end{tabular}
\caption{overall time} 
\label{table:overall_time}
\end{table}

\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 22\% & 57\% & 19\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 18\% & 63\% & 19\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 29\% & 48\% & 20\% & 2\% \\
	E3 & 19\% & 61\% & 18\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

@@

% impacts of making bridge page collapsed 
This is unclear.

% impacts of giving people advice on which transport to choose.
10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
5 people in the old interface chose meek as their second bridge (5/13, 38\%).
